Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-18 appendix.tex
sup

@@

\begin{comment}

 [T] By incorporating the idea of on-manifold adversarial example to
	adversarial training, the performance on benign example is greatly
	improved.
	%
	That idea can be interpreted as to be selective on the adversarial example
	used for trianing.
	%
	Here, in our observation, we are also selective on the adversarial examples
	used for training.
	%
	Is there anything in common?

[TODO LIST]

Before deadline

* Revise figures

* Revise manuscript

After deadline: supplementary

* add discussions and additional experiments
\end{comment}

>>>>

~\newline
\noindent\textbf{IV. Additional Notes on the Experimental Results}

@@
